Playground for PNAS cover graphic

### 2021-11-04 cover/cover.Rmd
New idea

```{r get-us, eval = FALSE}
sources <- c("jhu-csse", 
             "doctor-visits", 
             "chng", 
             "fb-survey", 
             "safegraph",
             "safegraph")

signals <- c("confirmed_7dav_incidence_prop",
             "smoothed_adj_cli",
             "smoothed_adj_outpatient_covid",
             "smoothed_whh_cmnty_cli",
             "bars_visit_prop",
             "restaurants_visit_prop")

start <- "2020-04-15"
end <- "2021-04-15"

@@

us <- covidcast_signals(
  sources, signals,
  start, end, 
  geo_type = "nation",
) %>% map(function(df) df %>% 
            Select(data_source, signal, geo_value, time_value, value))
```

```{r get-states, eval = FALSE}
state <- covidcast_signals(
  sources, signals,
  start, end, 
  geo_type = "state"
) %>% map(function(df) df %>% 
            Select(data_source, signal, geo_value, time_value, value))
```

```{r get-counties, eval = FALSE}
top_counties <- county_census %>%
  filter(COUNTY != 0) %>% # these are states
  arrange(desc(POPESTIMATE2019)) %>%
  head(n = 50) %>%
  pull(FIPS)

# Work around for an API problem: specifying geo_values in the API call fails on
# the CHNG data. So we filter after the fact instead. DANGER: Very slow.
county_nochng <- covidcast_signals(
  sources[sources != "chng"], signals[sources != "chng"],
  start, end, 
  geo_type = "county", geo_values = top_counties
) %>% map(function(df) df %>% 
            Select(data_source, signal, geo_value, time_value, value))

county_chng <- covidcast_signals(
  sources[sources == "chng"], signals[sources == "chng"],
  start, end, 
  geo_type = "county", 
) %>% map(function(df) df %>% 
            Select(data_source, signal, geo_value, time_value, value) %>%
            filter(geo_value %in% top_counties))

county <- append(county_nochng, county_chng)
```

@@

```{r build-sg}
# SafeGraph national signals don't exist for all time, so build them from states
y = state_census %>% 
  mutate(geo_value = tolower(ABBR)) %>% 
  rename(w = POPESTIMATE2019) %>%
  select(geo_value, w)

for (i in which(sources == "safegraph")) {  
  us[[i]] <- state[[i]] %>% 
    left_join(y, by = "geo_value") %>% 
    group_by(data_source, signal, time_value) %>%
    summarize(value = Sum(w * value) / Sum(w)) %>%
    mutate(geo_value = "us") %>%
    ungroup()
} 
```

```{r smooth-sg}
# SafeGraph signals at all levels aren't smoothed, so we use 7-day averaging
for (i in which(sources == "safegraph")) {  
  us[[i]] <- us[[i]] %>% 
    as.epi_tibble() %>% 
    group_by(geo_value) %>%
    epi_slide(~ Mean(.x$value), n = 7, new_col_name = "value") %>%
    ungroup()

  state[[i]] <- state[[i]] %>% 
    as.epi_tibble() %>% 
    group_by(geo_value) %>%
    epi_slide(~ Mean(.x$value), n = 7, new_col_name = "value") %>%
    ungroup()

  county[[i]] <- county[[i]] %>% 
    as.epi_tibble() %>% 
    group_by(geo_value) %>%
    epi_slide(~ Mean(.x$value), n = 7, new_col_name = "value") %>%
    ungroup() 
}
```

```{r aggregate-data}
all <- do.call(rbind, c(us, state, county))
```

```{r plotting-functions}
names <- c("Cases", 
           "DV-CLI", 
           "CHNG-COVID", 
           "CTIS-CLI-in-community",
           "SG-Bars", 
           "SG-Restaurants")

colors <- c("black", scales::hue_pal()(length(signals)-1))

get_trend_plot <- function(df) {
  case_min <- Min(df %>% filter(signal == signals[1]) %>% pull(value))
  case_max <- Max(df %>% filter(signal == signals[1]) %>% pull(value))

  df %>%
    group_by(signal, geo_value) %>%
    mutate(value = (value - Min(value)) / (Max(value) - Min(value)) * 
             case_max + case_min) %>%
    ungroup() %>%
    mutate(signal = factor(signal, levels = signals, labels = names)) %>%
    ggplot(aes(x = time_value, y = value, color = signal)) +
    geom_line() + scale_color_manual(breaks = names, values = colors) +
    facet_wrap(vars(geo_value), scales = "free_y") + 
    labs(x = "Date", y = "Signal value (scaled)") +
    theme_bw() + theme(legend.pos = "bottom", legend.title = element_blank())
}
```

```{r plot-it, fig.width = 10, fig.height = 4}
all %>%
  filter(signal != signals[5]) %>%
  filter(geo_value %in% c("us", "tx", "48113")) %>%
  filter(between(time_value, as.Date("2020-06-01"), as.Date("2020-07-15"))) %>%
  get_trend_plot()
```

>>>>

```{r get-data, eval = FALSE}
sources <- c("jhu-csse", 
             "doctor-visits", 
             "fb-survey", 
             "google-symptoms")

signals <- c("confirmed_7dav_incidence_prop",
             "smoothed_adj_cli",
             "smoothed_whh_cmnty_cli",
             "sum_anosmia_ageusia_smoothed_search")

start <- "2020-04-15"
end <- "2021-10-25"

@@

x <- covidcast_signals(
  sources, signals,
  start, end, 
  geo_type = "state"
) %>% map(function(df) df %>% 
            Select(data_source, signal, geo_value, time_value, value))
```

@@

```{r trend-plots}
names <- c("Reported COVID cases", 
           "COVID symptoms in medical claims", 
           "Self-reported COVID symptoms in surveys",
           "Searches for COVID symptoms on Google")
colors <- c("#FFFFFF", "#E69F00", "#56B4E9", "#CC79A7")

g <- vector(mode = "list", length = length(x))
delta <- 1/500
alpha <- 0.35
ylim <- c(-0.05, 1.05 + 50 * delta)

for (i in 1:length(x)) {
  g[[i]] <- x[[i]] %>%
    filter(geo_value %in% tolower(state.abb)) %>%
    mutate(geo_num = as.integer(as.factor(geo_value))) %>%
    group_by(geo_value) %>%
    mutate(value = (value - Min(value)) / (Max(value) - Min(value)) + 
             delta * (geo_num - 1)) %>%
    ungroup() %>%
    ggplot(aes(x = time_value, y = value, group = geo_value)) +
    labs(y = names[i]) + coord_cartesian(ylim = ylim) +
    geom_line(alpha = 0.5, color = colors[i]) + theme_void() +
    theme(panel.background = element_rect(fill = "black"),
          axis.title.y = element_text(color = colors[i], angle = 90,
                                      margin = margin(l = 10, r = -15)))
}

pdf(file = "cover-graphic.pdf", width = 15, height = 15)
do.call(gridExtra::marrangeGrob, list(g, nrow = 5, ncol = 1))
graphics.off()
```
